---
title: "Assignment 5"
author: "Ewelina Plachimowicz"
date: "4/28/2022"
output: html_document
---

## Exercise 3

Write names of all US states in UPPERCASE and lowercase to a file. Write how to do this without typing all 50 names manually. Separate code from input and from output.

```{r setup, include=FALSE}

# Loading required packages
library(datasets)

```

```{r}

# Reading states names from 'state' dataset ('datasets' library)
states_names <- state.name

# Creating new dataframe with names for all states
states_database <- data.frame(Id = c(1:length(states_names)), 
                              States_names = states_names, 
                              Uppercase_names = toupper(states_names), 
                              Lowercase_names = tolower(states_names))

```

```{r}

# Saving results to Excel file
write.csv(states_database, 'states_database.csv')

```

---

## Exercise 4

The code below is of poor quality. Improve it (you may rewrite it to R, if you find it more convenient). [Data (StudentsPerfomance.csv) is available on Kaggle.](https://www.kaggle.com/spscientist/students-performance-in-exams)

*note: the code contains comments to make you understand what you should do, even if you are not very familiar with Python. They may not be the best comments possible...*

```
# Importing required libraries
import pandas as pd
import matplotlib.pyplot as plt

# Read the file with data
studPerformance = pd.read_csv('StudentsPerformance.csv')

# We need to get list of all unique names of groups for column 'race/ethnicity'
groups_list = list(studPerformance['race/ethnicity'].unique())
# Also we need to sort that list alphabetically
groups_list = sorted(groups_list)
groups_list

# The dataframe contains data about 5 groups - A, B, C, D and E

# Printing mean math score for each group by loop
for i in groups_list:
  # Calculating mean math score for given group (i)
  mean_math_score = studPerformance[studPerformance['race/ethnicity'] == i]['math score'].mean()
  
  # Printing results
  print('Average math score for', i, 'is equal to:', mean_math_score, '\n')
  

# Print average value for math, reading, and writing tests for students who completed 
# the test preparation course and their parent obtained a degree

# List of values to filter students with parent who obtained a degree
degrees_list = ["associate's degree", "bachelor's degree", "master's degree"]

# Filtering students with completed course
degree_test = studPerformance[studPerformance['test preparation course'] == 'completed']
# Filtering students with parent who obtained a degree
degree_test = degree_test[degree_test['parental level of education'].isin(degrees_list)]

# List of columns to calculate the mean score
score_types = ['math score', 'reading score', 'writing score']

# Printing mean score for each test by loop
for i in score_types:
  # Calculating mean score for given test (i)
  mean_score = degree_test[i].mean()
  
  # Printing results
  print('Average', i, 'is equal to:', mean_score, '\n')


# Plot the histogram of math scores divided by reading scores for each student
plot_data = studPerformance['math score'] / studPerformance['reading score']

plt.hist(plot_data)
plt.xlabel('Count of students') # Setting x axis title
plt.ylabel('Math score / Reading score') # Setting y axis title
plt.title('Histogram of math score divided by reading score for each student') # Setting plot title
plt.show()
```