---
title: "Assignment 4"
author: "Ewelina Plachimowicz"
date: "4/23/2022"
output: html_document
---

## Exercise 1

Consider a [FizzBuzz problem](https://codegolf.stackexchange.com/questions/58615/1-2-fizz-4-buzz). The program should write numbers from 1 to 100, separated by a newline, but multiples of 3 and of 5 should be replaced with "Fizz" and "Buzz" respectively. For numbers which are multiples of both 3 and 5 print "FizzBuzz".

``` {r}

for (n in 1:100) {
  
  if (n%%3 == 0 & n%%5 != 0) { # Numbers that are divisible by 3, but not by 5
    cat('Fizz\n\n')
  } else if (n%%3 != 0 & n%%5 == 0) { # Numbers that are divisible by 5, but not by 3
    cat('Buzz\n\n')
  } else if (n%%3 == 0 & n%%5 == 0) { # Numbers that are divisible by 3 and 5
    cat('FizzBuzz\n\n')
  } else { # Other numbers
    cat(n, '\n\n')
  }
  
}

```

---

## Exercise 2

1. Write a function which takes *n* (float or integer) as a parameter and returns the largest Fibonacci number smaller than *n*. The function should be documented, with type hints, and appropriate comments.

``` {r}

fibonacci_number <- function(n) {
  # Fibonacci numbers - first number is equal to 0, second number is equal to 1, 
  # each next number is the sum of the previous two
  
  if (class(n) != 'numeric') {
    print('Choose an integer')
  } else if (n < 0) { 
    print('Number can not be below 0') # Fibonacci numbers starts from 0
  } else if (n == 0) { 
    print('Can not find Fibonacci number below 0') # Fibonacci numbers starts from 0
  } else if (n > 0 & n <= 1) {
    return(0)
  } else if (n > 1) {
    fibonacci_vector <- c(0, 1) # First two numbers are always the same
    
    # Loop stops calculating Fibonacci numbers when last number in vector is larger or equal to n
    while (fibonacci_vector[length(fibonacci_vector)] < n) {
      # Sum of the previous two Fibonacci numbers
      fibonacci_next_num <- fibonacci_vector[length(fibonacci_vector) - 1] + 
                            fibonacci_vector[length(fibonacci_vector)]
      # Adding number to the vector
      fibonacci_vector <- c(fibonacci_vector, fibonacci_next_num)
    }
    
    return(fibonacci_vector[length(fibonacci_vector) - 1]) # Returning penultimate number in the vector
  }
  
}

# Example
fibonacci_number(8)

```

2. Write a function which reverses digits in an integer number (for example 7245 -> 5427). The function should be documented, with type hints, and appropriate comments.

``` {r}

reverse_digits <- function(n) {
  
  if (class(n) != 'numeric') {
    print('Choose an integer')
  } else if (n < 0) {
    print('Number should be greater than or equal to 0')
  } else if (n == Inf) {
    print('Number can not be infinitive')
  } else {
    # rev() function - provides a reversed version of its argument
    # strsplit() function - split the elements of a character vector x into substrings
    
    n_reversed <- as.numeric(paste(rev(strsplit(as.character(n), "")[[1]]), 
                                   collapse = "")) # Calculating reversed number
    
    return(n_reversed)
  }
  
}

# Example
reverse_digits(1234)

```